Capon Beamforming Applied on Moving Objects - An Analysis of Local Shift-Invariance

### 2013-11-04 HRUIofMovingObjects/jrnl_article.tex
Moving objects paper: Done some writing. Added some references

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beam pairs. The point scatterer response has been simulated using Field II \comment{add citations} \comment{add table with simulation settings}. We see that the contours are approximately diagonal and therefore we can conclude that the system is locally lateral shift-invariant. The P-MAE and A-MAE are also minimal.

The scallop loss (max A-MAE) is smaller than what was predicted by Fig.\,\ref{fig:das_capon_beams}. To understand this note that Fig.\,\ref{fig:das_capon_beams} shows the one-way response of a passive array, and the system resolution has therefore been calculated based on the receive aperture only. Whereas the beamspacing in (\ref{eq:resolution}) is derived from the fact that the two-way lateral response of an active rectangular aperture is a $D_{tx}+D_{rx}$ wide triangle in K-space \comment{Cite Hergum et al. Simulation in K-space}. Even though the lateral bandwidth is increased, the distance to the first zero remains unchanged (The Rayleigh criteria) when multiplying two sinc functions. Sampling according to (\ref{eq:resolution}) is therefore more than what is strictly needed in practise. The loss in Fig.\,\ref{fig:das_shiftinvariant} is thus smaller than what was predicted.

In Fig.\,\ref{fig:das_shiftvariant} the beam spacing is reduced by a factor of two. We see that the scallop loss increases to a level where the contours no longer are diagonal. Hence, the imaging system is no longer locally lateral shift-invariant. We observe that the maximum peak is lost when the point is located between two beams and the distance between the beams are too high.

@@

The diagonal factor $d$ and the effective adaptive aperture size $L$ can be used to control the mainlobe width of the Capon beamformer. In both extreme cases, $d=inf$ \comment{add correct symbol} and $L=1$, the Capon beamformer becomes the DAS beamformer, and therefore requires a beamspacing according to (\ref{eq:resolution}). In Fig.\,\ref{fig:capon2} we show how the scallop loss is reduced when the amount of diagonal loading is increased. We observe that Fig.\,\ref{fig:capon2} contains the same pattern as present in Fig.\,\ref{fig:das_shiftvariant}. From Fig.\,\ref{fig:image_capon} it should be obvious that the Capon beamformer requires an increase in the lateral sampling in order to make the imaging system locally lateral shift-invariant, or the resolution has to be reduced to the same level as DAS. It would be unwise to do all the computation involved with Capon beamforming with a high $d$ value and end up with a resolution equal to DAS. However, we see that the diagonal factor can be a useful tool if resolution has to be traded for the need of oversampling.

@@

\section{Methods}
We will now discuss different ways to improve on the lateral shift-invariance when using the Capon beamformer. From the previous section it should now be clear that we somehow need to increase the lateral sampling. However, several questions still has to be answered. How should the oversampling be conducted, how large does the oversampling needs to be and how will the different methods affect the system frame rate?

\subsection{Oversampling on Transmit}
The typical way of obtaining sufficient sampling in an active broadband system is by increasing the number of transmit beams until (\ref{eq:resolution}) is fulfilled. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a factor two and ten respectively. As expected the scallop loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed in order to better see the beam-to-beam variation. Even though increasing the number of transmit improves the lateral shift-invariance it will also reduce the imaging frame rate with a factor equal to the oversampling factor. It is therefore not a feasible option for real time ultrasound imaging.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_2x_oversampling_2.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Oversampling on transmit ...}
\label{fig:capon_oversampling}
\end{figure*}

>>>>

Fig.\,\ref{fig:das_shiftinvariant} presents a LSV-plot for an imaging system using DAS beamforming with a beam spacing equal to (\ref{eq:resolution}). The red dotted vertical lines indicates the position of tx-rx beam pairs. The point scatterer response has been simulated using Field II \cite{Jensen1992, Jensen1996a} \comment{add table with simulation settings}. We see that the contours are approximately diagonal and therefore we can conclude that the system is locally lateral shift-invariant. The P-MAE and A-MAE are also minimal.

The scallop loss (max A-MAE) is smaller than what was predicted by Fig.\,\ref{fig:das_capon_beams}. To understand why note that Fig.\,\ref{fig:das_capon_beams} shows the one-way response of a passive array, and the system resolution has therefore been calculated based on the receive aperture only. Whereas the beamspacing in (\ref{eq:resolution}) is derived from the fact that the two-way lateral response of an active rectangular aperture is a $D_{tx}+D_{rx}$ wide triangle in K-space \cite{Hergum2009}. Even though the lateral bandwidth is increased, the distance to the first zero (The Rayleigh criteria) remains the same when multiplying two sinc functions. Sampling according to (\ref{eq:resolution}) is therefore more than what is strictly needed in practise. The loss in Fig.\,\ref{fig:das_shiftinvariant} is because of this smaller than what was predicted.

In Fig.\,\ref{fig:das_shiftvariant} the beam spacing is reduced by a factor of two. We see how the scallop loss is now increased to a level where the contours no longer are diagonal. Hence, the imaging system is no longer locally lateral shift-invariant. We observe that the maximum peak is lost when the point is located between two beams and the distance between the beams are too high.

@@

The diagonal factor $d$ and the effective adaptive aperture size $L$ can be used to control the mainlobe width of the Capon beamformer. In both extreme cases, $d=\infty$ and $L=1$, the Capon beamformer becomes the DAS beamformer, and will require a beamspacing according to (\ref{eq:resolution}). In Fig.\,\ref{fig:capon2} we show how the scallop loss is reduced when the amount of diagonal loading is increased. We observe that Fig.\,\ref{fig:capon2} contains the same pattern as present in Fig.\,\ref{fig:das_shiftvariant}. From Fig.\,\ref{fig:image_capon} it should be obvious that the Capon beamformer either require an increase in the lateral sampling in order to make the imaging system locally lateral shift-invariant, or the resolution has to be reduced to the same level as DAS. It would be unwise to do all the computation involved with Capon beamforming with a high $d$ value and end up with a resolution equal to DAS. However, we see that the diagonal factor can be a useful tool if resolution has to be traded for the need of oversampling.

@@

\section{Methods}
We will now discuss different ways to improve on the lateral shift-invariance when using the Capon beamformer. From the previous section it should now be clear that we somehow need to increase the lateral sampling. We will investigate how this oversampling should be conducted, how large it needs to be and how the different methods will affect the system frame rate.

\subsection{Oversampling on Transmit}
The typical way of obtaining sufficient sampling in an active broadband system is by increasing the number of transmit beams until (\ref{eq:resolution}) is fulfilled. In Fig.\,\ref{fig:capon_oversampling_a} and Fig.\,\ref{fig:capon_oversampling_b} we have increased the lateral sampling on transmit by a factor four and ten respectively. As expected the scallop loss decreases with increased lateral sampling. Note that Fig.\,\ref{fig:capon_oversampling_b} is zoomed in order to better see the beam-to-beam variation. Even though increasing the number of transmit improves the lateral shift-invariance it will also reduce the imaging frame rate with a factor equal to the oversampling factor. It is therefore not a feasible option for real time ultrasound imaging.

@@

\begin{figure*}[!t]
\centerline{
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_4x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_a}
}
\subfloat[]{
\includegraphics[width=0.5\linewidth]{\img capon_L=32_K=1_d=001_10x_oversampling_2_zoomed.eps}\label{fig:capon_oversampling_b}
}
}
\caption{Oversampling on transmit ...}
\label{fig:capon_oversampling}
\end{figure*}
